Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-12-08 Paper.Rmd
fixed pedagog fig2 as instructed

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm,height=8 cm]{./Results/copula_pedagog_fig_BB1.pdf}
\caption{(A-C) Data generated using the BB1 copula (Methods) with three different 
sets of parameters chosen to produce a variety of 
lower-tail (LT) and upper-tail (UT) dependence strengths (Methods), but the same 
Kendall correlation (to two digits) in all cases. (D-F) Similar to A-C, but
with stronger correlation. Asymmetry of tail dependence (LT-UT) is the same 
within each column of panels.\label{fig_cop_pedag}}
\end{center}
\end{figure}
<!--***DAN: Shya, please reduce it to three panels in each row (the middle one and the most extreme ones), while keeping the panels the same size, and label the panels A-F. Please also get rid of the title over each panel, and express the UT and LT values to two digits, and make the font slightly bigger for those as well as for the axis labels and numbers. Please also remove the 
color - we don't need it and it would cost us a lot of money.-->

>>>>

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm,height=8 cm]{./Results/copula_pedagog_fig_BB1.pdf}
\caption{(A-C) Data generated using the BB1 copula (Methods) with three different 
sets of parameters chosen to produce a variety of 
lower-tail (LT) and upper-tail (UT) dependence strengths (Methods), but the same 
Kendall correlation (KC) (to two digits) in all cases. (D-F) Similar to A-C, but
with stronger correlation. Asymmetry of tail dependence (LT-UT) is the same 
within each column of panels.\label{fig_cop_pedag}}
\end{center}
\end{figure}
<!--***DAN: Shya, please reduce it to three panels in each row (the middle one and the most extreme ones), while keeping the panels the same size, and label the panels A-F. Please also get rid of the title over each panel, and express the UT and LT values to two digits, and make the font slightly bigger for those as well as for the axis labels and numbers. Please also remove the 
color - we don't need it and it would cost us a lot of money.
***Shya: Done.-->

### 2018-12-08 SupportingInformation.Rmd
fixed pedagog fig2 as instructed

pdf("./Results/copula_pedagog_fig_BB1.pdf",height=8,width=20)
op<-par(mfrow=c(2,5),mar=c(3,3,3,3), mgp=c(1.5,0.5,0))

desLTmUT_vector<-c(-0.4,-0.2,0,0.2,0.4)
#parlist<-list(c(0.2,1.5),c(0.2,1.1),c(0.2,1.5),c(0.5,1.1),c(0.5,1.5))
#for(i in 1:length(desLTmUT_vector)){
#  print(i)
#  iLmU<-desLTmUT_vector[i]
#  call_optim<-optim(par=parlist[[i]],fn=f,destau=0.4,desLTmUT=iLmU,fam=7,method = "BFGS")
#  call_optim$par
#  c<-BiCopSim(N=500,family=7,par=call_optim$par[1],par2=call_optim$par[2])
#  plot(c[,1],c[,2],col="blue",xlab="u",ylab="v",cex.lab=2,cex.axis=1.5)
#  mtext(paste0("tau = 0.4", ", LTmUT = ",iLmU,sep=""),side=3)
#}

for(i in desLTmUT_vector){
  # print(i)
  destau<-0.5
  call_optim<-optim(par=c(0.2,1.5),fn=f,destau=destau,desLTmUT=i,fam=7,method = "BFGS")
  obj<-BiCop(family=7,par=call_optim$par[1],par2=call_optim$par[2])
  c<-BiCopSim(N=500,obj)
  plot(c[,1],c[,2],col="blue",xlab="u",ylab="v",cex.lab=2,cex.axis=1.5)
  mtext(paste0("tau = ",round(obj$tau,5),", ( LT - UT ) = ",round((obj$taildep$lower - obj$taildep$upper),5),sep=""),side=3)
  legend("topleft",paste0("UT=",round(obj$taildep$upper,5)),bty="n",cex=1.5,text.col="magenta")
  legend("bottomright",paste0("LT=",round(obj$taildep$lower,5)),bty="n",cex=1.5,text.col="magenta")
}

for(i in desLTmUT_vector){
 # print(i)
  destau<-0.8
 call_optim<-optim(par=c(0.2,1.5),fn=f,destau=destau,desLTmUT=i,fam=7,method = "BFGS")
 obj<-BiCop(family=7,par=call_optim$par[1],par2=call_optim$par[2])
 c<-BiCopSim(N=500,obj)
 plot(c[,1],c[,2],col="red",xlab="u",ylab="v",cex.lab=2,cex.axis=1.5)
 mtext(paste0("tau = ",round(obj$tau,5),", ( LT - UT ) = ",round((obj$taildep$lower - obj$taildep$upper),5),sep=""),side=3)
 legend("topleft",paste0("UT=",round(obj$taildep$upper,5)),bty="n",cex=1.5,text.col="magenta")
 legend("bottomright",paste0("LT=",round(obj$taildep$lower,5)),bty="n",cex=1.5,text.col="magenta")
}

>>>>

pdf("./Results/copula_pedagog_fig_BB1.pdf",height=8,width=12)
op<-par(mfrow=c(2,3),mar=c(8,8,1.5,3), mgp=c(5,2,0))

desLTmUT_vector<-c(-0.4,0,0.4)

for(i in c(1:length(desLTmUT_vector))){
  # print(i)
  destau<-0.5
  call_optim<-optim(par=c(0.2,1.5),fn=f,destau=destau,desLTmUT=desLTmUT_vector[i],fam=7,method = "BFGS")
  obj<-BiCop(family=7,par=call_optim$par[1],par2=call_optim$par[2])
  c<-BiCopSim(N=500,obj)
  plot(c[,1],c[,2],col="grey",xlab="u",ylab="v",cex.lab=3.5,cex.axis=3.5)
  legend("topleft",LETTERS[i],bty="n",cex=4,x.intersp=-0.5)
  #mtext(paste0("( LT - UT ) = ",round((obj$taildep$lower - obj$taildep$upper),2),sep=""),side=3,cex=2)
  legend("bottomright",c(paste0("KC= ", round(obj$tau,2)),
                                    paste0("LT=",round(obj$taildep$lower,2)),
                                    paste0("UT=",round(obj$taildep$upper,2))),bty="n",horiz = F,cex=2.5)
  #legend("bottomright",paste0("LT=",round(obj$taildep$lower,2)),bty="n",cex=2)
}

for(i in c(1:length(desLTmUT_vector))){
 # print(i)
  destau<-0.8
 call_optim<-optim(par=c(0.2,1.5),fn=f,destau=destau,desLTmUT=desLTmUT_vector[i],fam=7,method = "BFGS")
 obj<-BiCop(family=7,par=call_optim$par[1],par2=call_optim$par[2])
 c<-BiCopSim(N=500,obj)
 plot(c[,1],c[,2],col="grey",xlab="u",ylab="v",cex.lab=3.5,cex.axis=3.5)
 legend("topleft",LETTERS[3+i],bty="n",cex=4,x.intersp=-0.5)
 #mtext(paste0("( LT - UT ) = ",round((obj$taildep$lower - obj$taildep$upper),2),sep=""),side=3,cex=2)
  legend("bottomright",c(paste0("KC= ", round(obj$tau,2)),
                                    paste0("LT=",round(obj$taildep$lower,2)),
                                    paste0("UT=",round(obj$taildep$upper,2))),bty="n",horiz = F,cex=2.5)
 #legend("bottomright",paste0("LT=",round(obj$taildep$lower,2)),bty="n",cex=2)
}
